Results

### 2023-03-02 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
described results for MLM

To investigate whether ER strategies require cognitive effort, we conducted an rmANOVA comparing the subjective effort ratings of four strategies (active viewing, distraction, distancing, suppression).
We found a significant effect of strategy (`r papaja::apa_print(SubjEffort_aov)$full_result`, `r papaja::apa_print(SubjEffort_BF)$statistic`).
Post-hoc test showed significant higher subjective effort for distraction ($\eta_{p}^{2}=`r papaja::printnum(SubjEffort_con[1,8:9])`$, $BF_{10}=$ `r papaja::printnum(SubjEffort_con[1,7], format = "e")`), distancing ($\eta_{p}^{2}=`r papaja::printnum(SubjEffort_con[2,8:9])`$, $BF_{10}=$ `r papaja::printnum(SubjEffort_con[2,7], format = "e")`), and suppression ($\eta_{p}^{2}=`r papaja::printnum(SubjEffort_con[3,8:9])`$, $BF_{10}=$ `r papaja::printnum(SubjEffort_con[3,7], format = "e")`) compared to active viewing.
Moreover, we found significantly lower effort during suppression compared with distraction ($\eta_{p}^{2}=`r papaja::printnum(SubjEffort_con[5,8:9])`$, $BF_{10}=$ `r papaja::printnum(SubjEffort_con[5,7], format = "e")`) and distancing ($\eta_{p}^{2}=`r papaja::printnum(SubjEffort_con[6,8:9])`$, $BF_{10}=$ `r papaja::printnum(SubjEffort_con[6,7])`).

@@

The predictors effort ($p=$ `r papaja::printnum(summary(MLM_2)$coefficients[1,5])`), ...

>>>>

To investigate whether ER strategies require cognitive effort, we conducted an rmANOVA comparing the subjective effort ratings of four strategies (active viewing, distraction, distancing, suppression).
We found a significant effect of strategy (`r papaja::apa_print(SubjEffort_aov)$full_result`, `r papaja::apa_print(SubjEffort_BF)$statistic`).
Post-hoc test showed significant higher subjective effort for distraction (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X3distraction`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "3_distraction"],progress = FALSE, paired = TRUE))$statistic`), distancing (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X4distancing`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "4_distancing"],progress = FALSE, paired = TRUE))$statistic`), and suppression (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X5suppression`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],progress = FALSE, paired = TRUE))$statistic`) compared to active viewing. 
Moreover, we found significantly lower effort during suppression compared with distraction (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X3distraction_X5suppression`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "3_distraction"], y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],progress = FALSE, paired = TRUE))$statistic`) and distancing (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X4distancing_X5suppression`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "4_distancing"], y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],progress = FALSE, paired = TRUE))$statistic`).

@@

The predictors effort rating (`r papaja::apa_print(MLM_2)$full_result$effort_cwc`), utility rating (`r papaja::apa_print(MLM_2)$full_result$effort_cwc`), and *Corrugator* activity (`r papaja::apa_print(MLM_2)$full_result$effort_cwc`) showed a significant association with SVs.
The values were relatively small, so the respective effect size $f^{2}$ was calculated as the explained variance.
Interestingly, utility rating showed the greatest effect size of all predictors ($f^{2}=$ `r papaja::printnum(H5_M2_table[4,5], digits = 3)`), indicating that utility rating explained `r papaja::printnum(H5_M2_table[4,5]*100, digits = 1)` percent of variance in SVs. 
Effort rating showed an effect size of $f^{2}=$ `r papaja::printnum(H5_M2_table[2,5], digits = 3)`.
The effect sizes of all other predictors were negligibly small ($f^{2}< 0.01$).
